### 2014-03-17 docs/paper/paper.tex
clock implications

A hardware implementation of the Nengo-RT design was produced on a Xilinx VC707 development board, which includes a modern field-programmable gate array (FPGA)
device (Xilinx XC7VX485T-2FFG1761C). This device was chosen because of its ready availability on a development platform and its large logic capacity and available resources.
In particular, it provides 37~080~Kb of on-chip block RAM and 2~800 customizable DSP slices, both of which the Nengo-RT design requires in abundance in order to support
the largest possible implementation size.

@@

\item FPGA resources utilized; maximum theoretical design size
\item clock speed and implications of this
\item Ethernet communication for control and I/O -- maximum channel capacity in terms of DVs

>>>>

A hardware implementation of the \design{} design was produced on a Xilinx VC707 development board, which includes a modern field-programmable gate array (FPGA)
device (Xilinx XC7VX485T-2FFG1761C). This device was chosen because of its ready availability on a development platform and its large logic capacity and available resources.
In particular, it provides 37~080~Kb of on-chip block RAM and 2~800 customizable DSP slices, both of which the Nengo-RT design requires in abundance in order to support
the largest possible implementation size.

@@

\item FPGA resources utilized; maximum theoretical design size
\item clock speed and implications of this

The implemented hardware operates at a clock speed of 125~MHz, using the same extermal clock source as the Gigabit Ethernet PHY.
This is convenient as it means that the entire design, including both the simulator hardware and the I/O interfaces, operates from the same clock source.
Because of this, there is no latency when receiving input or transmitting output to and from the simulation;
if two different clock speeds were used, extra buffers would have to be implemented in order to ``cross'' the two clock domains,
and the logic operating in the faster clock domain would occasionally have to wait for the slower-clocked logic to consume input from the buffer.
This type of stall would prevent part of the simulator from operating in real-time; by using the same clock for all logic, however, this problem is averted and
both input and output are wait-free.

\item Ethernet communication for control and I/O -- maximum channel capacity in terms of DVs
